---
title: "Bigdata"
output: html_document
date: '2022-05-16'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r,include=FALSE}
library(tidyverse)
library(scatterplot3d)
library(dplyr)
library(plotly)
library(mclust)
library(ggplot2)
```

```{r,include=FALSE}
path2 <- "/home/ubuntulab/data-sample/"
temp2 <- list.files(path = path2, pattern = "part-*")
```

```{r,include=FALSE}
Output_Table2 <-tibble()
for(i in 1:length(temp2)){
  table2 <- tryCatch(read.delim(paste(path2,toString(temp2[i]), sep=""), header = FALSE, sep = ","),error = function(e) NULL)
  Output_Table2 <- bind_rows(Output_Table2, table2)
}

Output_Table2$V3 <- gsub('{1}.$', '', Output_Table2$V3)
Output_Table2$V1 <- substring(Output_Table2$V1, 2)
```

# Plotting the the sample data
The plot of the sample data gives insight about the data. This help us to know patterns in our data and identify outliers. 

```{r}
scatterplot3d(Output_Table2, pch = 16,color = "red",
              main="sample data",
              xlab = "inp. side Accelerometer",
              ylab = " out accelerometer",
              zlab = "Tachnometer reading")

```
```{r}
Output_Table2 %>% 
  ggplot(aes(V1,V3))+
  geom_point(color = "blue")+
  xlab("input side Accelerometer")+
  ylab("Tachnometer reading")+
  labs(title="2D feature plot")
  
```

```{r}
Output_Table2 %>% 
  ggplot(aes(V1,V2))+
  geom_point(color = "blue")+
  xlab("input side Accelerometer")+
  ylab("output accelerometer")+
  labs(title="2D feature plot")
  
```
```{r}
Output_Table2 %>% 
  ggplot(aes(V2,V3))+
  geom_point(color = "blue")+
  xlab("output accelerometer")+
  ylab("Tachnometer reading")+
  labs(title="2D feature plot")
  
```

# The elbow plot
 
The elbow plot is helpful when determining the optimal number of clustering (k). We see from the plot that the error rate increases after 2

```{r}
Output_Table2[,1:3] <- sapply(Output_Table2[,1:3], as.numeric)
k.max <- 10
wss <- sapply(1:k.max, 
              function(k){kmeans(Output_Table2, k, nstart=50,iter.max = 15 )$tot.withinss})
plot(1:k.max, wss,
     main="Elbow plot for optimal k",
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total within-clusters SS")

```



```{r,include=FALSE}
path <- "/home/ubuntulab/kmeans-sample/"
temp <- list.files(path = path, pattern = "part-*")
```

```{r,include=FALSE}
Output_Table<-tibble()
for(i in 1:length(temp)){
  table <- tryCatch(read.delim(paste(path,toString(temp[i]), sep=""), header = FALSE, sep = ","),error = function(e) NULL)
  Output_Table <- bind_rows(Output_Table, table)
}
Output_Table
```

# Clustering plot 



```{r}
colors <- c("#56B4E9", "#E69F00")
colors <- colors[as.factor(Output_Table$V1)]
ss3d <- scatterplot3d(Output_Table[,2:4], pch = 16, color = colors,angle = 55,
              main="Gearbox clustering result",
              xlab = "inp. side Accelerometer",
              ylab = " out accelerometer",
              zlab = "Tachnometer reading")

legend(ss3d$xyz.convert(-10, -4, 0.5), legend = c('C1','C2'),
      col =  c("#56B4E9", "#E69F00"), pch = 16)
```

```{r,include=FALSE}
path1 <- "/home/ubuntulab/anomalies-sample/"
temp1 <- list.files(path = path1, pattern = "part-*")
```

```{r,include=F}
Output_Table1 <-tibble()
for(i in 1:length(temp1)){
  table1 <- tryCatch(read.delim(paste(path1,toString(temp1[i]), sep=""), header = FALSE, sep = ","),error = function(e) NULL)
  Output_Table1 <- bind_rows(Output_Table1, table1)
}

Output_Table1$V3 <- gsub('{1}.$', '', Output_Table1$V3)
Output_Table1$V1 <- substring(Output_Table1$V1, 2)
```


```{r,include=F}
new_df <- Output_Table1
```


```{r,include=F}
new_df <- new_df%>% 
  rename(
    V2 = V1,
    V3 = V2,
    V4 = V3
    )
```

# Annomaly plots

```{r,include=F}
new_df["V1"] <- "2"
new_df[,1:3] <- sapply(new_df[,1:3], as.numeric)

```

```{r,include=F}
new_df$V1 <- as.integer(new_df$V1)
```


```{r,include=F}
merge_df <- merge(Output_Table,new_df,by = c("V1","V2","V3","V4"), all= T)

```


```{r,include=FALSE}
library(rgl)
library(ggplot2)
library(rglwidget)
```
```{r,include=FALSE}
merge_df$V1 <- as.factor(merge_df$V1)
```


```{r}
colors <- c("#56B4E9", "#E69F00", "red")
colors <- colors[as.factor(merge_df$V1)]
s3d <- scatterplot3d(merge_df[,2:4], pch = 16, color = colors,angle = 55,main="Anomally detection",
              xlab = "inp. side Accelerometer",
              ylab = " out accelerometer",
              zlab = "Tachnometer reading")
legend(s3d$xyz.convert(-10, -8, 4.5), legend = c('C1','C2','Ano'),
      col =  c("#56B4E9", "#E69F00", "red"), pch = 16)
```


# 2D plot after cludtering and anommalies

Here we tried to detect the anomaly from the 2D plot. This helps to know the variables that that have outliers when plotted against each other. Here the 0 and 1 represent the cluster and 2 is the anomaly for each plot

```{r}
merge_df %>% 
  ggplot(aes(V2,V3, color = V1))+
  geom_point()+
  labs(fill = "cluster")+
  theme(legend.title = element_blank())+
  xlab("input side accelerometer")+
  ylab("output accelerometer")
  
```

```{r}
merge_df %>% 
  ggplot(aes(V2,V4, color = V1))+
  geom_point()+
  theme(legend.title = element_blank())+
  xlab("input side accelerometer")+
  ylab("Tachnometer reading")
```


```{r}
merge_df %>% 
  ggplot(aes(V3,V4, color = V1))+
  geom_point()+
  theme(legend.title = element_blank())+
  xlab("output accelerometer")+
  ylab("Tachnometer reading")

```







